---
title: "ST405-Mini Project"
author: "S/18/824"
date: "2024-05-21"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading the necessary packages
```{r}
library(tidyverse)
library(mvnormtest)
library(CCA)
library(ggplot2)
library(skimr)
library(psych)
library(GGally)
library(CCP)

```

Import the data set
```{r}
mmreg<-read_csv("../data/mmreg.csv")
head(mmreg)
```
```{r}
glimpse(mmreg)
```
This data set have records of 600 rows and 8 columns.

```{r}
str(mmreg)
```
check for missing values
```{r}
sum(is.na(mmreg))
```
In this data set no any missing values.


Summary of the above data set
```{r}
summary(mmreg)
skim(mmreg)
```

```{r}

mshapiro.test(t(mmreg))
```


Standardized the variables.Because these are in different scale
```{r}
# Standardize the variables
standard_mmreg_data <- as.data.frame(scale(mmreg))

# Display the first few rows of the standardized data
head(standard_mmreg_data)

```
Perform canonical correlation analysis
##Separate the data set into two sets of variables: psychological variables and academic variables.
```{r}
# psychological variables
psychology <- standard_mmreg_data[, c(1:3)]

# academic
academic <- standard_mmreg_data[, c(4:8)]

# View the transformed data
head(psychology)
head(academic)

```

Check the correlation among variables in psychology varaibles set
```{r}
ggpairs(psychology)
```
Check the correlation among variables in academic varaibles set
```{r}
ggpairs(academic)
```
Correlation between two sets
```{r}
correlation <- matcor(psychology,academic)
correlation
img.matcor(correlation,type = 3)
```
Canonical correlation model
```{r}
cano_corr_model <- cc(psychology,academic)

```
Canonical correlations
```{r}
cano_corr_model$cor
```
raw canonical coefficients
```{r}
cano_corr_model[3:4]
```
compute canonical loadings
```{r}
cano_loadings <- comput(psychology, academic, cano_corr_model)

# display canonical loadings
cano_loadings[3:6]
```

Test the significance of canonical correlations
```{r}
rho <- cano_corr_model$cor
n <- dim(psychology)[1]
p <- length(psychology)
q <- length(academic)

#Wilk's test
p.asym(rho,n,p,q,tstat = "Wilks")
```


Lawley-Hotelling test
```{r}
p.asym(rho,n,p,q,tstat = "Hotelling")
```

Pillai's test
```{r}
p.asym(rho,n,p,q,tstat = "Pillai")
```

Roy's largest root test
```{r}
p.asym(rho,n,p,q,tstat = "Roy")
```


Test the independence between two sets of variables
```{r}
result <- cancor(psychology,academic)
r_squared <- result$cor * result$cor
r_squared
```
```{r}
# standardized psychological canonical coefficients diagonal matrix of psychology sd's
s1 <- diag(sqrt(diag(cov(psychology))))
s1 %*% cano_corr_model$xcoef

```
```{r}
# standardized academic canonical coefficients diagonal matrix of academic sd's
s2 <- diag(sqrt(diag(cov(academic))))
s2 %*% cano_corr_model$ycoef

```


